\documentclass{crortiz_cv_2021}

\setname{Carlos}{Ortiz-Gómez}
\setmobile{+1 857 472 1960}
\setmail{orgoca@gmail.com}
\setposition{Data Scientist} %ignored for now
\setlinkedinaccount{https://www.linkedin.com/in/orgoca/} %you can play with color of the template (red is also nice..)
\setgithubaccount{https://github.com/orgoca} %you can play with color of the template (red is also nice..)
\definecolor{udemy}{RGB}{235, 82, 79}
\setthemecolor{udemy} %you can play with color of the template (red is also nice..)
\usepackage{multicol}

\begin{document}
%Set variables
%You can add sections, texts, explanations just by copying the style below. Replace the dummy texts "\lipsum[1][x-x]\par" with actual texts.
%Create header
\headerview
\vspace{1ex}
%Sections
%
% Summary
\addblocktext{Summary}{%
\\Senior professional with expertise in data science, entrepreneurship, energy, program management, and team building. I am known for delivering large impact projects and driving innovation in highly visible organizations. My key areas of interest in data science are democratization of data in organizations (augmenting experts decision making capabilities through analytics, data visualization, dashboards and smart interfaces), statistical analysis (hypothesis testing, experiments and quasi-experimental methods), translating business problems into actionable data strategies, and communicating data through visualization and storytelling.\ %replace this part with actual text
}
%
% Skills
\section{Skills}
    %
    \newcommand{\skillone}{\createskill{Programming Languages:}{\ \  R \cpshalf Python \cpshalf Julia \ \ \textbf{\emph{Libraries:}} \ \  Shiny \cpshalf Tidyverse \cpshalf GGplot2 \cpshalf Scikitlearn \cpshalf Pandas }}
    %
    \newcommand{\skilltwo}{\createskill{Statistics:}{Causal Inference \cpshalf Hypothesis Testing \cpshalf Experimental Design \cpshalf Statistical Learning}}
    %
    \newcommand{\skillthree}{\createskill{Data Engineering (ETL):}{\textbf{\emph{Experienced:}} \ \  SQL \ \ \textbf{\emph{Familiar:}} \ \  Kafka \cpshalf Spark \cpshalf Docker \cpshalf Hadoop \cpshalf Google Cloud}}
    %
    \newcommand{\skillfour}{\createskill{Management:}{PM/PGM \cpshalf Negotiation \cpshalf Public Speaking \cpshalf Team Building \cpshalf Strategic Planning}}
    %
    \newcommand{\skillfive}{\createskill{Interfaces \& Visualization:}{Design Thinking \cpshalf Front End Dev \cpshalf Shiny Dashboards \cpshalf Python Dash}}
    %
    \newcommand{\skillsix}{\createskill{Data Publications:}{RMarkdown \cpshalf  Jupyter Notebooks \cpshalf LaTeX \cpshalf R Presentations \cpshalf Power Point}}
    %
    \newcommand{\skillseven}{\createskill{Languages:}{\textbf{\emph{Native:}} \ \  Spanish  \ \ \textbf{\emph{Fluent:}} \ \ English \ \ }}
    %
    \createskills{\skillone, \skilltwo, \skillthree, \skillfour, \skillfive, \skillsix, \skillseven}
%

% Experience
\section{Experience}
    %
    \datedexperience{Kossina Cloud}{12/2020- / Queretaro, MX} 
    \explanation{Founding Partner and Chief Technology Officer}
    \explanationdetail{\coloredbullet\ %
     \ Kossina Cloud is a data driven dark kitchen model. From a single kitchen with no dining room, we serve 20 different food brands through third party delivery platforms. %replace this part with actual text
     }
    \explanationdetail{\coloredbullet\ %
     \ I lead the development of and end-to-end data science platform with modules for: sales and production analytics, operations management, client clustering and recommendation systems, market intelligence, incremental sales analysis (A/B Testing). %replace this part with actual text
     }
    %
    \datedexperience{Yoomy Analytics}{06/2020-12/2020 / Aventura, FL} 
    \explanation{Founding Partner and Chief Data Scientist} 
    \explanationdetail{\coloredbullet\ %
     \ YoomyAnalytics is a data and analytics solution for medium-sized restaurant chains. We provide dashboard and analytics solutions to restaurants that want to leverage their data to advance their businesses. %replace this part with actual text
     }
    \explanationdetail{\coloredbullet\ %
     \ Design and implementation of analytics solutions and dashboards developed with R Shiny. %replace this part with actual text
     }
    %
    \datedexperience{AIPatentsMX}{06/2019-12/2020 / Aventura,FL} 
    \explanation{Founding Partner and Startup CEO} 
    \explanationdetail{\coloredbullet\ %
     \ Led end to end development of software solutions to accelerate patent examination: Interviewed nearly 50 examiners, comprehensively mapping patent examination and classification processes. Used design thinking iterations to conceptualize automation and AI augmentation tools for patent examiners. %replace this part with actual text
     }
    %
    \datedexperience{Mexico's Department of Energy ( \href{https://www.gob.mx/sener}{SENER} )}{12/2012-05/2018 / Mexico City, MX} 
    \explanation{Director General (DG) for Science and Talent Development (2016:18) \cpshalf DG for Information (2012:16)} 
    \explanationdetail{\emph{Responsible for the research \& development, and talent development agenda for Mexico’s energy sector.} %replace this part with actual text
     }
    \explanationdetail{\coloredbullet\ %
     \ Crowd sourced the national energy community to produce the ‘National Priorities in Research and Talent Development for the Energy Sector’ publication series. These documents guide Mexican national research efforts on topics like clean hydrocarbons, accelerated discovery of clean energy materials, smart grids and grid-scale electric energy storage. %replace this part with actual text
     }
    \explanationdetail{\coloredbullet\ %
     \ Conceptualized and launched the national level ‘Strategic Program for Human Resource Development’ which accomplished the following: (a) 2,500+ postgraduate scholarships for students in global graduate programs on energy research and technology. (b) \$300 million USD+ invested in capacity building for training and research in topics aligned with national energy research priorities. (c) 30,000+ K12 students from underprivileged schools around the country participating in our ‘Ciencias para Compartir’ program. %replace this part with actual text
     }
    \explanationdetail{\coloredbullet\ %
     \ Launched the ‘Mexican Centers for Energy Innovation’ (CEMIEs) in the topics of wind, solar and geothermal energy. To date, this effort has grown to a total of ten CEMIEs. (over USD 110 million investments. %replace this part with actual text
     }
    \explanationdetail{\coloredbullet\ %
     \ As Director General for Information, I led the development of the National System for Energy Information, which sourced data from energy companies and regulators for the purpose of reporting public energy information according to the International Energy Agency membership requirements. %replace this part with actual text
     }
    %
    \datedexperience{Mexico's 'National Electricity and Clean Energy Institute' ( \href{https://www.gob.mx/ineel}{INEEL} )}{08/2016-05/2018 / Morelos, MX} 
    \explanation{Deputy Chairman of the Board / Chair of the Directors Board} 
    \explanationdetail{\coloredbullet\ %
     \ Led the efforts to rebuild a professional board with business orientation (vs previous academic orientation); as well as to recruit and onboard the Chief Executive Officer (Diego Arjona Arguelles). %replace this part with actual text
     }
    \explanationdetail{\coloredbullet\ %
     \ Recruited, onboarded, and launched the energy storage group (focusing on organic redox flow batteries). %replace this part with actual text
     }
    \datedexperience{Alianza Fiidem / Comimsa}{04/2010-07/2012 / Mexico City, MX} 
    \explanation{Senior Consultant} 
    %
    \explanationdetail{\coloredbullet\ %
     \ Advise in the design and implementation of the 'Energy Sustainability R\&D Fund': recruited and trained a Project Management Office, designed and launch of the first call for proposals, and formalized the first cohort of state sponsored projects in clean tech R\&D in Mexico for the Secretary of Energy of Mexico. %replace this part with actual text
     }
    \datedexperience{Grupo Salinas}{06/2009-04/2010 / Mexico City, MX} 
    \explanation{Lead for Latin America Energy Projects} 
    %
    \explanationdetail{\coloredbullet\ %
     \ Led the energy efficiency strategy for Grupo Salinas in the group’s Iusacell (mobile network operator) and TV Azteca (television network) facilities. Performed numerous energy audits at the group’s facilities and identified a portfolio of investment projects involving energy conservation measures. %replace this part with actual text
     }
    \datedexperience{Arup North America Limited}{11/2007-03/2009 / Los Angeles, CA} 
    \explanation{Project Manager Senior \cpshalf Energy Engineer} 
    \explanationdetail{\coloredbullet\ %
     \ Energy master planning for urban redevelopments like Cornfields Arroyo Seco in Los Angeles, CA, the Bayview Area Redevelopment project in San Francisco CA (Hunters Point and Candlestick Point). %replace this part with actual text
     }
    %
%
%Education
\section{Education} 
    \datedexperience{UNIVERSITY OF CALIFORNIA, BERKELEY, School of Information}{Online Masters, 2020-2022} 
    \explanation{\href{https://ischoolonline.berkeley.edu/data-science/curriculum/}{Master of Information and Data Science}} 
    \explanationdetail{\coloredbullet\ %
     \ Part time online program that allows me to \textbf{work full time}.  }%
    \datedexperience{HARVARD UNIVERSITY / John F. Kennedy School of Government}{Cambridge, MA, 2018-2019}
    \explanation{\href{https://www.hks.harvard.edu/educational-programs/masters-programs/mid-career-master-public-administration}
    {Master in Public Administration / Data Science}} 
     \explanationdetail{\coloredbullet\ % 
     \ Specialization in Data Science in Policy Making \& Public Administration.\par} %
    \datedexperience{UNIVERSITY OF SOUTH FLORIDA, School of Engineering}{Tampa, FL, 2002-2006} 
    \explanation{Bachelor of Science in Mechanical Engineering} 
    \explanationdetail{\coloredbullet\ %
     \ Winner of the Capstone class of 2006, ‘Excellence in Design’ and ‘Excellence in Teamwork’ Awards. %
     
     }
%
%Certifications
\section{Certifications} 
    \datedexperience{HARVARD UNIVERSITY / John F. Kennedy School of Government}{Issued May 2019 / No Expiration Date}
    \explanation{\href{http://www.hksmldarea.com/certificate/}{Certificate in Management, Leadership and Decision Sciences}} 
%

% Experience
\section{What Inspires Me?}
    \begin{multicols}{2}
    \newcommand{\extrasone}{%
    \ Food \& FoodTech
    }
    %
    \newcommand{\extrastwo}{%
    \ Education \& EdTech
    }
    %
    \newcommand{\extrasthree}{%
    \ Data Driven Decisions
    }
    %
    \newcommand{\extrasfour}{%
    \ International Development \& Econometrics
    }
    %
    \newcommand{\extrasfive}{%
    \ RStudio \cpshalf Udemy \cpshalf 3Blue1Brown \cpshalf Aspuru-Guzik
    }
    %
    \newcommand{\extrassix}{%
    \ Inspiring, Ambitious \& Committed People 
    }
    \newcommand{\extrasseven}{%
    \ Intellectual Property \& Patents 
    }
    \newcommand{\extraseight}{%
    \ My wife Gabriela and our kids Nicolas \& Melissa 
    }
    \newcommand{\listofextrass}{\extrasone, \extrastwo, \extrasthree, \extrasfour, \extrasfive, \extrassix, \extrasseven, \extraseight}
    %
    \createbullets{\listofextrass}
    \end{multicols}
%

% Experience
\section{Additional Information}
    \newcommand{\extraone}{%
    \ Eligible for work with NAFTA TN Visa (No sponsorship needed) \cpshalf Immediate availability
    }
    %
    \newcommand{\listofextras}{\extraone}
    \createbullets{\listofextras}
%

%Footnote
\createfootnote
\end{document}
